Effects of CHILDREN's programs

### 2020-02-25 paper.Rnw
Imputed variables can take values in between integers between 0 and 4

\documentclass[12pt, a4paper]{article}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
\usepackage{floatrow}
\usepackage[hidelinks]{hyperref}
\usepackage{rotating}
% \usepackage[authoryear]{natbib}
% \bibliographystyle{apalike}
\usepackage{mathtools}
\usepackage[onehalfspacing]{setspace}
\usepackage[left = 72 pt, right = 72 pt]{geometry}

@@

\title{Effects of CHILDREN's programs}
\author{Laura Huber, Laura Jepsen, Jonathan Kirschner, Rafael Schütz, Yannick Zurl}
\date{27th February 2020}

@@

@@

@@

@@

A1\\ 
Cumulative Odds Regression 
Outliers?

@@

A2\\
Partition

@@

\printbibliography
\end{document}

>>>>

\documentclass[12pt, a4paper]{article}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
\usepackage{floatrow}
\usepackage[hidelinks]{hyperref}
\usepackage{rotating}
% \usepackage[authoryear]{natbib}
% \bibliographystyle{apalike}
\usepackage{mathtools}
\usepackage[onehalfspacing]{setspace}
\usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}

@@

\title{Effects of CHILDREN's programs}
\author{Laura Huber, Laura Jepsen, Jonathan Kirschner, Rafael Schütz (11574909), Yannick Zurl}
\date{27th February 2020}

@@

\begin{abstract} 
abstract on separate page
100 - 150 words
\end{abstract}

@@

the introduction should include: motivation, precise research questions, very short literature review, most important results, further proceedings

@@

\section{Conclusion}

\printbibliography

@@

\subsection{A1: Cumulative Odds Regression}

Outliers?

@@

\subsection{A2: Partition}

@@

\{Ehrenwörtliche Erklärung aller Teilnehmer}

\end{document}
